%-------------------------------------------------------------------------------
% CURRICULUM VITAE
% Author: Igor Andruskiewitsch
% Description: My Curriculum Vitae
%-------------------------------------------------------------------------------

\documentclass{curriculum}
\begin{document}

%-------------------------------------------------------------------------------
%   HEADER
%-------------------------------------------------------------------------------

\begin{cvheader}

\makeheader
    {Igor Andruskiewitsch}  {\email{i.andruskiewitsch23@gmail.com}}
    {Senior iOS Engineer}    {\github{rusito-23}}
    {C\'ordoba, Argentina}    {\linkedin{igor-andruskiewitsch}}

\end{cvheader}

%-------------------------------------------------------------------------------
%   PROFESSIONAL SUMMARY
%-------------------------------------------------------------------------------

\begin{cvsection}{Professional Summary}

    \begin{summary}
        Experienced iOS Engineer with over 6 years of expertise in \textbf{Swift with UIKit and SwiftUI}. Proven track record in developing scalable mobile solutions for \textbf{FinTech and E-commerce}. Passionate about delivering high-quality software and improving development processes.
    \end{summary}

\end{cvsection}

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EDUCATION
%-------------------------------------------------------------------------------

\begin{cvsection}{Education}

    \makesectionitemheader
        {Computer Science Bachelor eq.}       {FaMAF, UNC}
        {Analista en Computaci贸n}             {C\'ordoba, Argentina}
    \begin{sectionitemlist}
        \item {\textbf{GPA}: 8.4 (10 scale)}
        \item {\textbf{Graduation Date}: July 2021}
        \item {\textbf{Relevant Coursework}: Data Structures \& Algorithms, Software Engineering, Numerical Analysis, Neural Networks.}
    \end{sectionitemlist}

\end{cvsection}

%-------------------------------------------------------------------------------
%   EXPERIENCE
%-------------------------------------------------------------------------------

\begin{cvsection}{Experience}

    %---------------------------------------------------------------------------
    %   SECTION ITEM: Bitso
    %---------------------------------------------------------------------------

    \makesectionitemheader
        {Bitso}                     {May 2024 - present}
        {Senior Software Engineer}  {Remote - Full Time Employee}

        \begin{sectionitemlist}
        \item{
                \textbf{Technologies:} Swift (iOS), React Native, UIKit, SwiftUI, Java Spring, PostgreSQL
            }
        \item{
            Implemented multiple experiments that contributed to a
            high increase in the \textbf{Earnings feature activation}.
        }
        \item{
            Delivered several UX enhancements, including a
            \textbf{historical earnings analysis tool} for mobile.
        }
        \item{
            Contributed to the migration of several
            \textit{Design System components} to SwiftUI and React Native.
        }
        \end{sectionitemlist}

    %---------------------------------------------------------------------------
    %---------------------------------------------------------------------------
    %   SECTION ITEM: eBay - Distillery
    %---------------------------------------------------------------------------

    \makesectionitemheader
        {eBay - Distillery}         {March 2023 - May 2024}
        {Senior iOS Engineer}       {Remote - Contractor}

        \begin{sectionitemlist}
        \item{
            \textbf{Technologies:} Swift (iOS), MVVM-C pattern, UIKit, SwiftUI, Combine
        }
        \item{
            Integrated a \textbf{Post-Purchase Recommendation System} to increase customer engagement, enhancing revenue.
        }
        \item{
            Worked on multiple flows to enhance the seller payout experience,
            including \textbf{Debit Card Payouts} and \textbf{Bank Information Collection}.
        }
        \item{
            Successfully migrated several Objective-C components, increasing the Swift component coverage from 80\% to 100\%.
        }
        \end{sectionitemlist}

    %---------------------------------------------------------------------------
    %   SECTION ITEM: Venmo - Taller
    %---------------------------------------------------------------------------

    \makesectionitemheader
        {Venmo (PayPal) - Taller Technologies}      {Sept. 2020 - Jan. 2023}
        {Senior Software Engineer}                  {Remote - Contractor}

        \begin{sectionitemlist}
        \item{
            \textbf{Technologies:} Swift (iOS), MVVM-C pattern, RxSwift, UIKit,
            Python, Django, Kubernetes, DataDog, ElasticSearch
        }
        \item{
            Improved the security for \textbf{business profiles}
            by developing an \textit{ad-hoc Biometric and PIN Authentication system}.
        }
        \item{
            Developed several features to improve the \textit{Discovery and Promotion}
            of business profiles, such as adding support for photo galleries
            and showcasing business profiles in the feed.
        }
        \item{
            Participated in the effort to ensure the app was \textbf{a11y} compliant
            by conducting bug searches, analysis and resolution.
        }
        \item{
            Introduced \textbf{charity profiles} to the app by adding support
            for \textit{Search and Discovery} and \textit{Donations}.
        }
        \item{
            Automated fix to replace wrongly set images to 200k users with
            picture comparison using structural similarity.
        }
        \end{sectionitemlist}

    %---------------------------------------------------------------------------
    %   SECTION ITEM: IncluIT / SimTLIX
    %---------------------------------------------------------------------------

    \makesectionitemheader
        {IncluIT / SimTLIX}                    {Jun. 2019 - Sept. 2020}
        {Semi Senior Software Engineer}        {C贸rdoba, Argentina}

        \begin{sectionitemlist}
        \item{
            \textbf{Technologies:} Swift \& Objective-C (iOS \& macOS), C++,
            Python, Keras, TensorFlow Lite.
        }
        \item{
            Migrated Firewall from \textit{Kernel Extensions} to \textit{Network Extension framework}
            for VPN application \textbf{Pulse Secure}.
        }
        \item{
            Developed a real-time background blur PoC for the video
            conference application \textbf{Avaya Workspace}.
        }
        \item{
            Re-wrote the authentication library for the \textbf{Personal}
            (telecommunications company) app.
        }
        \end{sectionitemlist}

    %---------------------------------------------------------------------------
    %   SECTION ITEM: Globant / Royal Caribbean
    %---------------------------------------------------------------------------

    \makesectionitemheader
        {Globant - Royal Caribbean}            {Feb. 2019 - Jun. 2019}
        {iOS Engineer}                         {C贸rdoba, Argentina}

        \begin{sectionitemlist}
        \item{Improved code coverage by adding \textbf{unit tests} using \textbf{Swift}.}
        \item{Improved code style and quality by fixing \textbf{SwiftLint} issues.}
        \end{sectionitemlist}

    %---------------------------------------------------------------------------
    %   SECTION ITEM: JCOR
    %---------------------------------------------------------------------------

    \makesectionitemheader
        {JCOR}                               {Jun. 2018 - Feb. 2019}
        {Full Stack Developer}               {C贸rdoba, Argentina}

        \begin{sectionitemlist}
        \item{
            \textbf{Technologies:} Java Spring (back-end), Swift (iOS), Java (Android)
            Groovy on Rails, Javascript, MySQL, PostgreSQL.
        }
        \item{
            Developed car-pooling flows and refactored login and register for the
            \textbf{Taaxii} transportation company.
        }
        \item{
            Improved stability by automating test cases using
            \textbf{Selenium} and \textbf{Appium}.
        }
        \end{sectionitemlist}

\end{cvsection}

%-------------------------------------------------------------------------------
%   EXTRACURRICULAR ACTIVITIES
%-------------------------------------------------------------------------------

\begin{cvsection}{Extracurricular Activities}
    \begin{sectionitemlist}
        \item {Volunteered to help the committee in the \textbf{PyData} 2018 \& 2019 editions}
        \item {Received a scholarship to participate in the 2017 \textbf{Conference on Computer Science} at the National University of Rosario, Argentina}
        \item {Participated in the Argentinian Programming Contest, \textbf{TAP}, 2018 \& 2019 editions}
    \end{sectionitemlist}
\end{cvsection}

%-------------------------------------------------------------------------------
%   END
%-------------------------------------------------------------------------------

\end{document}
